Preregistration

### 2019-05-04 analysis/survey/preregistration.Rmd
Nicer LaTeX
No confirmatory analyses
Clean up metadata

---
title: "Results"
author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
---

See Chaudhry and Heiss (2019) preregistration for reference: <https://osf.io/dx973>

@@

$$
\begin{aligned}
\beta &\sim \text{MVN}(Z \Gamma, \xi) \\
y &\sim \text{MNL}(X \beta, \varepsilon)
\end{aligned}
$$

@@

TODO: Do we do this?

COMMENT: No, it's really just looking at/comparing the posterior marginals on their own vs. the posterior marginals with different covariates includes, plus the market simulation.

>>>>

---
title: "Preregistration"
author: "Andrew Heiss, Marc Dotson, and Suparna Chaudhry"
---

@@

$$
\begin{aligned}
\beta &\sim \operatorname{Multivariate} \mathcal{N}(Z \Gamma, \xi) \\
y &\sim \operatorname{Multinomial logit}(X \beta, \varepsilon)
\end{aligned}
$$

@@
